# TIL: dplyr subchain
Today I learned (TIL) in R stats you can make subchains for `dplyr` syntax to use elsewhere in your code.  Take this vanilla `dplyr` example below.

```{r vanilla, echo=TRUE, message=FALSE, warning=FALSE}
library(dplyr)
starwars %>%
  group_by(species) %>%
  summarise(n = n(), mass = mean(mass, na.rm = TRUE)) %>%
  filter(n > 1)
```

Suppose I want to pull out a particular piece of this `dplyr` chain.  I can save it with the `.` notation and reuse it elswhere.

``` {r subchain}
summ <- . %>% summarise(n = n(), mass = mean(mass, na.rm = TRUE))

starwars %>%
  group_by(species) %>%
  summ %>%
  filter(n > 1)
```

This is is very useful for functions where you can first configure a subchain based on the functions parameters and then call it elsewhere throughout your function.  You can see where I have done so [in my `svytldr` function here](https://github.com/AJThurston/svytldr/blob/main/R/svytldr.R) in lines 36 through 60 to configure a svy dsgn object based on the presence of `ids`, `strata`, and `weights` parameters. Hat tip to [this stackoverflow answer](https://stackoverflow.com/questions/65559994/how-to-reuse-parts-of-long-chain-of-pipe-operators-in-r) that finally answered this question for me.

My implementation is below and linked above:
```{r svytldr, echo=TRUE, message=FALSE, warning=FALSE, eval = FALSE}
...
  if (!missing(ids) && !missing(weights) && !missing(strata)){
    dsgn <- . %>% as_survey_design(ids = ids, weights = weights, strata = strata)
  }
  if (!missing(ids) && missing(weights) && !missing(strata)){
    dsgn <- . %>% as_survey_design(ids = ids, strata = strata)
    }
  if (!missing(ids) && !missing(weights) && missing(strata)){
    dsgn <- . %>% as_survey_design(ids = ids, weights = weights)
  }
  if (!missing(ids) && missing(weights) && missing(strata)){
    dsgn <- . %>% as_survey_design(ids = ids)
  }
  if (missing(ids) && !missing(weights) && !missing(strata)){
    dsgn <- . %>% as_survey_design(weights = weights, strata = strata)
  }
  if (missing(ids) && missing(weights) && !missing(strata)){
    dsgn <- . %>% as_survey_design(strata = strata)
  }
  if (missing(ids) && !missing(weights) && missing(strata)){
    dsgn <- . %>% as_survey_design(weights = weights)
  }
  if (missing(ids) && missing(weights) && missing(strata)){
    dsgn <- . %>% as_survey_design()
  }
... 
res <- df %>%
  dsgn %>%
  group_by(as.factor("overall"), df[, i], .drop = FALSE) %>%
  summarize(m = survey_mean(), n = unweighted(n()))
```


